Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-17 jss/article.tex
Added barplot
[skip ci]

\begin{figure}
	\centering
	\caption{Representation of the enriched modules (first ten rows), either with either Bonferroni correction or no correction. Grey tiles means that the data is not available for this module in this sample. P-values of low signifance are in white, whereas p-values of high significance are represent in blue. }
	\includegraphics{figures/comparison_corrected_unc.pdf}
\end{figure}

>>>>

\begin{figure}
	\centering
	\caption{Representation of the enriched modules (first ten rows), either with either Bonferroni correction or no correction. Grey tiles means that the data is not available for this module in this sample. P-values of low significance are in white, whereas p-values of high significance are represent in blue. Samples are in abscissa and modules are on the Y axis  }
	\includegraphics{figures/comparison_corrected_unc.pdf}
\end{figure}

\begin{figure}
	\caption{Representation of the enriched modules (first ten rows), either with either Bonferroni correction (left) or no correction (right). The modules are on the X axis and the p-values are on the Y axis.  }
	\includegraphics{figures/comparison_corrected_unc_bars.pdf}
\end{figure}
